%-------------------------
% Jaxson Pahukula's Resume
% made from template: https://github.com/jakegut/resume
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}
\usepackage[T1]{fontenc}
\usepackage[default]{raleway}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}
% \usepackage{concmath}
% \usepackage[scaled]{beraserif}
% \usepackage[T1]{fontenc}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
      \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
    \item\small{
        {#1 \vspace{-2pt}}
    }
}

\newcommand{\resumeSubheading}[4]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & #2 \\
        \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
        \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[1]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
        \small#1 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Jaxson Pahukula} \\ \vspace{1pt}
    \small (808) 740-5007 $|$ \href{mailto:jaxpahu@gmail.com}{\underline{jaxpahu@gmail.com}} $|$ \href{https://jaxsonp.com}{\underline{jaxsonp.com}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
    \resumeSubHeadingListStart
        \resumeSubheading
        {Purdue University}{West Lafayette, IN}
        {Pursuing B.S. in Computer Science, systems programming concentration}{Aug. 2022 -- May 2025 (est)}
    \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

    \resumeSubheading
        {Griffiss Institute, VICEROY Maven Program}{Summer 2024}
        {Research Intern}{Rome, NY}
        \resumeItemListStart
        \resumeItem{Participated in cybersecurity lessons with various Department of Defense (DoD) personnel on Air Force and DoD-oriented cyber missions.}
        \resumeItem{Was selected to represent VICEROY and P3I at the Pentagon in a meeting with HON Shyu (OUSD(R\&E)) and dialogued with the offices of Hawai’i's senators and congressmen/women in Washington DC.}
        \resumeItem{Worked on a research project with the Air Force Research Lab.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
        {Applied Research Laboratory at the University of Hawai’i}{Summer 2023}
        {Software Dev Asst. / Intern}{Kihei, HI}
        \resumeItemListStart
            \resumeItem{Collaborated on a team researching new technologies for portal software for the DoD’s vanguard high performance computing center.}
            \resumeItem{Developed backend software for a mock central administration platform for managing containerized software on servers and swarms with Python, Flask, and Docker.}
        \resumeItemListEnd

     \resumeSubheading
        {Data Science Labs, Calculus II}{Jan. 2023 -- Dec. 2023}
        {Lab Instructor / TA}{West Lafayette, IN}
        \resumeItemListStart
            \resumeItem{Taught students to apply concepts from Calculus I and II to basic data science problems in a lab setting}
            \resumeItem{Led students in engaging lab projects using Jupyter notebooks, Python, Raspberry Pis, and various prototyping electronic components.}
            \resumeItem{Collaborated with other instructors and superiors to develop and refine the course curriculum.}
        \resumeItemListEnd

    \resumeSubheading
        {The Data Mine, Purdue University}{Aug. 2023 -- May 2024}
        {Undergraduate Data Science Researcher}{West Lafayette, IN}
        \resumeItemListStart
            \resumeItem{Collaborated with Raytheon Technologies to create a hard drive remaining-useful-life prediction model.}
            \resumeItem{Applied various data science procedures and techniques such as anomaly detection, k-means clustering, LSTM models, and more.}   
        \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart
    \resumeProjectHeading
        {\textbf{DIY Graphics Rendering Pipeline} $|$ \emph{C++}}
        \resumeItemListStart
            \resumeItem{A software renderer with mesh rendering, lighting, texture mapping, reflections, and more.}
            \resumeItem{Written fully from scratch for Purdue's CS33400, a graphics programming class.}
        \resumeItemListEnd
    \resumeProjectHeading
        {\textbf{FactoryScript} $|$ \emph{Rust}}
        \resumeItemListStart
            \resumeItem{An interpreted, dynamically-typed, gag programming language  (esolang) themed around factories.}
            \resumeItem{Programs (\textit{factories}) are graphs with nodes (\textit{stations}) connected by Unicode box characters (\textit{conveyor belts}).}
        \resumeItemListEnd
    \resumeProjectHeading
        {\textbf{University Simple C Compiler} $|$ \emph{C++, LLVM}}
        \resumeItemListStart
            \resumeItem{A top-down recursive descent compiler written for Purdue's CS 35200, a compilers class.}
            \resumeItem{Compiles University Simple C, an LL(1) toy subset of C, to LLVM IR with various custom optimization passes.}
        \resumeItemListEnd
    \resumeProjectHeading
        {\textbf{Beat Ballot} $|$ \emph{React, MUI, SQLite, Flask}}
        \resumeItemListStart
            \resumeItem{A web app where users create collaborative Spotify playlists with friends, voting on songs to add or remove.}
            \resumeItem{Created for a hackathon (Boilermake XI) in 36 hours.}
        \resumeItemListEnd
    \resumeProjectHeading{\textbf{And more...} Read about them at \href{https://jaxsonp.com}{\underline{jaxsonp.com}}}
\resumeSubHeadingListEnd

%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, C, Rust, C++, Java, Javascript, HTML/CSS, SQL, R} \\
     \textbf{Dev Environments/Tools}{: Git, Docker, UNIX, Jupyter, Visual Studio, IntelliJ } \\
     \textbf{Libraries}{: React, Flask, NumPy, Matplotlib, Pandas}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
